Will it blend: Is the Milky Way bar causing chaotic fanning of the Ophiuchus stream?

### 2015-08-21 ms.tex
added to methods

>>>>

We use ...
[Bulge from Portail et a. (2015), bar from Wegg and Gerhard (2015)?]

Though these density distributions are analytic and relatively simple, the potential and accelerations must be computed numerically. Rather than solve Poisson's equation at every evaluation of the potential or forces, we instead use the Self-Consistent Field (SCF) method \citep{hernquist92} to expand the density and potential on a series of orthogonal potential-density pairs. This method has been previously used to represent the potential from the Galactic bar \citep{zhao96, wangzhao12}. The advantage to this method is that the expansion coefficients (expensive integrals) only need to be computed once.

We follow the formalism introduced in \cite{hernquist92} and used in \cite{lowing11}:
